Toward Resolved Simulations of Burning Fronts in Thermonuclear X-ray Bursts

### 2018-09-26 astronum_2018/astronum-xrb.tex
update

Other ways to make the simulation less expensive can include a subgrid model,
even something as simple as subzone burning.\MarginPar{need the paper ref fo rthis}

Finally, we can try hybrid model approaches where the fully
compressible simulation can act as a subgrid model.  \MarginPar{this ties into Ann's stuff, and also the stuff Alice was doing}

>>>>

Within the realm of compressible hydrodynamics, there are a number of other techniques that 
should be explored. 
smarter refinement with AMR + hydrostatic refinement
well-balanced method to allow ultralow resolution to slide along with the burning front
higher-order
This are all

Other ways to make the simulation less expensive can include a subgrid model,
even something as simple as subzone burning.\MarginPar{need the paper ref fo rthis}
This is harder...

Finally, we can try hybrid model approaches where the fully
compressible simulation can act as a subgrid model.  \MarginPar{this ties into Ann's stuff, and also the stuff Alice was doing}
Multiscale methods can combine different hydro models together to allow 
for a full star simulation with resolved burning.  Examples include...
